Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-28 Papers/ms.tex
Fixed minor error
Pictures of sources and images

The estimated marginal likelihood of our model
is
$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -6967$, and
the information (Kullback-Leibler divergence from the prior to the posterior)
is $\mathcal{H} \approx 129$ nats.

>>>>

The estimated marginal likelihood of our model
is
$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -6967$, and
the information (Kullback-Leibler divergence from the prior to the posterior)
is $\mathcal{H} \approx 129$ nats. 
Three example models (lens and source) sampled from the posterior are shown
in Figure~\ref{fig:sources}.

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{sources.pdf}
\caption{Three example sources (and the corresponding lensed, blurred images)
representative of the posterior distribution. All three lens system scenarios
have substructures, which cause subtle distortions from the usual shape of
the caustics and critical curves (plotted as black curves).
The angular scales are 3 arcseconds for the sources and 15
arcseconds for the images.
\label{fig:sources}}
\end{center}
\end{figure}
